Modelling BCG vaccination in the UK

### 2019-07-31 rmds/09-model-fitting.Rmd
model fitting captions updated

```{r 09-age-strat-incidence, fig.scap = "Observed and predicted TB incidence stratified by model age group", fig.cap = "Observed and predicted TB incidence stratified by model age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. The model underpredicted incidence in all age groups fitted too with older adults have the best fit."}
knitr::include_graphics(file.path(plots_path, "overview-states-1990-age-1.png"))
```

@@

```{r 09-prior-posterior, warning = FALSE, message = FALSE}
sum_prior_posterior %>% 
  set_names(., nm = . %>% 
              str_replace("or", "or (95\\\\%CI)")) %>%
  mutate(Parameter = latex_param) %>% 
  select(-latex_param) %>% 
kable(
  caption.short = "Observed versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observerd versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. (95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.",
  booktabs = TRUE, longtable = TRUE, escape = FALSE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  {.}
```

@@

```{r 09-fig-sens, fig.scap = "Partial rank correlation coefficients for each parameter fitted too.", fig.cap = "Partial rank correlation coefficients for each parameter fitted too. Parameter names in figure are in their coded form. They can be interpreted as the following parameters:  $\\beta_{\\text{young adult}}$, $c_{\\text{eff}}$, $c^{\\text{hist}}_{\\text{eff}}$, $c^{\\text{hist}}_{\\text{half}}$, $M$, $M_{\\text{young adult}}$, $E_{\\text{syst}}$, $E_{\\text{noise}}$, $\\iota_{\\text{scale}}$, and $\\epsilon^{\\text{older-adult}}_L$", out.width = "200px"}
knitr::include_graphics(file.path(plots_path, "incidence-sensitivity-1.png"))
```

@@

Whilst the results presented here are not encouraging it may be the case that with a greatly extended runtime a much better fitting model may be found. The first step to testing this is to rerun the pipeline using several orders of magnitude more rejuvernation steps - as these have no RAM overhead. Even if the resulting model fits are still poor this may indicate areas for improvement - in either the model fitting pipeline or the model itself. An alternative option is to recode the model developed in the last chapter into a more generic form (i.e C) and to attempt to fit the model using other techniques that are less compute intensive and more robust - such as SMC-ABC. Another option would be to reimplement the model in the form required by another modelling package - such as `pomp`. However, this would mean running the risk of again getting stuck within a framework that is difficult to debug and may not be working as expected. A final option would be to reduce the complexity of the model and potentially fit to less complex data. This may be the only solution if the current model is not identifiable.

>>>>

```{r 09-age-strat-incidence, fig.scap = "Observed and predicted TB incidence stratified by model age group", fig.cap = "Observed and predicted TB incidence stratified by model age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. The darker ribbon identifies the interquartile range, whilst the lighter ribbon indicates the 2.5% and 97.5% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-states-1990-age-1.png"))
```

@@

```{r 09-prior-posterior, warning = FALSE, message = FALSE}
sum_prior_posterior %>% 
  set_names(., nm = . %>% 
              str_replace("or", "or (95\\\\%CI)")) %>%
  mutate(Parameter = latex_param) %>% 
  select(-latex_param) %>% 
kable(
  caption.short = "Prior and posterior medains for fitted model parameters", 
  caption = "Prior and posterior medains for fitted model parameters. (95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.",
  booktabs = TRUE, longtable = TRUE, escape = FALSE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  {.}
```

@@

```{r 09-fig-sens, fig.scap = "Partial rank correlation coefficients for each parameter fitted too.", fig.cap = "Partial rank correlation coefficients for each parameter fitted too. Parameter names in figure are in their coded form. They can be interpreted as the following parameters:  $\\beta_{\\text{young adult}}$, $c_{\\text{eff}}$, $c^{\\text{hist}}_{\\text{eff}}$, $c^{\\text{hist}}_{\\text{half}}$, $M$, $M_{\\text{young adult}}$, $E_{\\text{syst}}$, $E_{\\text{noise}}$, $\\iota_{\\text{scale}}$, and $\\epsilon^{\\text{older-adult}}_L$", out.width = "300px"}
knitr::include_graphics(file.path(plots_path, "incidence-sensitivity-1.png"))
```

@@

Whilst the results presented here are not encouraging it may be the case that with a greatly extended runtime a better fitting model may be found. The first step to testing this is to rerun the pipeline using several orders of magnitude more rejuvernation steps - as these have no RAM overhead. Even if the resulting model fits are still poor this may indicate areas for improvement - in either the model fitting pipeline or the model itself. An alternative option is to recode the model developed in the last chapter into a more generic form (i.e C) and to attempt to fit the model using other techniques that are less compute intensive and more robust - such as SMC-ABC. Another option would be to reimplement the model in the form required by another modelling package - such as `pomp`. However, this would mean running the risk of again getting stuck within a framework that is difficult to debug and may not be working as expected. A final option would be to reduce the complexity of the model and potentially fit to less complex data. This may be the only solution if the current model is not identifiable.

### 2019-07-31 rmds/10-model-results.Rmd
model fitting captions updated

```{r 10-overall-scenarios-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-future-1.png"))
```

```{r 10-table-future-incidence}
sum_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "", 
  caption = "(95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 10-age-scenarios-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-future-age-1.png"))
```

@@

```{r 10-scenarios-deaths-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-1.png"))
```

```{r 10-table-deaths-preds}
sum_deaths_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "", 
  caption = "(95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 10-age-scenarios-deaths-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-age-1.png"))
```
### Summary

>>>>

```{r 10-overall-scenarios-fig, fig.scap = "Forecast TB incidence for each scenario evaluated from 2005 to 2040", fig.cap = "Forecast TB incidence for each scenario evaluated from 2005 to 2040. Scenarios are differentiated by colour. The darker ribbon for each colour identifies the interquartile range, whilst the lighter ribbon indicates the 2.5% and 97.5% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-future-1.png"))
```

```{r 10-table-future-incidence}
sum_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Forecast overall TB incidence for each scenario evaluated from 2005 to 2040.", 
  caption = "Forecast overall TB incidence for each scenario evaluated from 2005 to 2040. For brevity only 5 year intervals are shown. (95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 10-age-scenarios-fig, fig.scap = "Forecast TB incidence for each scenario evaluated from 2005 to 2040, stratified by age group.", fig.cap = "Forecast TB incidence for each scenario evaluated from 2005 to 2040, stratified by age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. Scenarios are differentiated by colour. The darker ribbon for each colour identifies the interquartile range, whilst the lighter ribbon indicates the 2.5% and 97.5% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-future-age-1.png"))
```

@@

```{r 10-scenarios-deaths-fig, fig.scap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group.", fig.cap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group. Scenarios are differentiated by colour. The darker ribbon for each colour identifies the interquartile range, whilst the lighter ribbon indicates the 2.5% and 97.5% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-1.png"))
```

```{r 10-table-deaths-preds}
sum_deaths_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Forecast overall TB mortality for each scenario evaluated from 2005 to 2040.", 
  caption = "Forecast overall TB mortality for each scenario evaluated from 2005 to 2040. For brevity only 5 year intervals are shown.(95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 10-age-scenarios-deaths-fig, fig.scap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group, stratified by age group.", fig.cap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. Scenarios are differentiated by colour. The darker ribbon for each colour identifies the interquartile range, whilst the lighter ribbon indicates the 2.5% and 97.5% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-age-1.png"))
```
### Summary
